ST563 Final Project

### 2021-03-12 ST563-FP.Rmd
save

```{r pairs}
# Create pairwise scatterplots
pairs(wine[,c(2,5,7,8,9,10,11)])
```
Based on the pairwise scatterplots, we suspect that pH may be linearly correlated with density, sulphates, and alcohol. This leads me to believe that there is some relationship between the chemical properties of the wines. The following correlation plot gives a numeric summary of the linear relationship between the variables.

@@

# Conclusion

>>>>

```{r pairs, fig.align="center", out.width='4in', out.height='3.5in'}
# Create pairwise scatterplots
pairs(wine[,c(2,5,7,8,9,10,11)])
```
Based on the pairwise scatterplots, we suspect that pH may be linearly correlated with density, sulphates, and alcohol. This leads me to believe that there is some relationship between the chemical properties of the wines. The following correlation plot gives a numeric summary of the linear relationship between the variables.

@@

# Conclusion  
Hotels often suffer losses in revenue due to room vacancies that result from cancellations. Hotels can implement stringent cancellation policies as well as overbooking procedures to try and mitigate this loss in revenue. As analytics solutions are becoming more and more popular in the agriculture industry, we sought to apply machine learning learning models in an attempt to find . Hotel managers could use the results of a machine learning algorithm to take action based on knowledge of forecasted cancellations or demand.

Based on the results of our study, we were able to predict the cancellation of a given room with about 75-80% accuracy. Although this is a *good* result considering the non-information rate of 54%, it is by no means excellent. These results indicate that machine learning algorithms could be a good technique for predicting cancellations, but that there is room for improvement. With a more formal, industry expert-guided variable selection process, we believe that higher prediction accuracies can be achieved. Machine learning models could potentially be combined with other techniques to help optimize revenue from bookings.
